\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-24 ms.tex
eddie comments

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
\label{fig:decam-field}
\end{figure}

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.

\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was needed for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to the instrumental photometry---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---to put our photometry on the PS1/DECam system.
This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands.
}

\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the $g$-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
We note that the smaller over-density located northeast of the \decam\ field, component b (see \figurename~\ref{fig:cmds}), was not followed up in this work.

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
}
\startdata
% $u$  &  \nodata & $2.178 \pm  0.016$ &     \nodata \\
% $g$  & $g-r$ & $-0.05287 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
% $i$   &  $i-z$ & $-0.24665 \pm 0.0011$ &     $-0.07379 \pm 0.00069$
$u_{\rm DECam}$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
$g_{\rm PS1}$  & $g_{\rm inst.}-i_{\rm inst.}$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
$i_{\rm PS1}$   &  $g_{\rm inst.}-i_{\rm inst.}$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
\enddata
\end{deluxetable}
\end{center}

@@

While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
\changes{In addition, uncertainty in the \gaia\ passbands can cause significant differences in \gaia\ \bprp\ color for very blue sources \citep{MAW:2018}.}
To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
We use the $g$- and $i$-band photometry \changes{(and $u$-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.

>>>>

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-field.pdf}
\caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ g-band follow up (blue and red markers).
Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
\label{fig:decam-field}
\end{figure}

We obtained \decam\ u-, g-, and i-band imaging of a single field centered on the ``a'' spatial component of the cluster (see \figurename~\ref{fig:cmds}) discovered using the \gaia\ data (see previous section).  Observations were obtained with the Dark Energy Camera (DECam) on the CTIO 4m Blanco telescope on UT 2018 May 20 with 3$\times$300s
exposures in $u-$, $g-$, and $i$-band.  The NOAO Community Pipeline (CP; \citealt{Valdes:2014}; Valdes et al., in preparation) InstCal images, which have the instrumental signature removed, were downloaded from the NOAO Archive\footnote{\url{http://archive.noao.edu}} for further processing.  Forced PSF photometry was performed with the PHOTRED pipeline \citep{Nidever:2017} which uses the DAOPHOT ALLSTAR \citep{Stetson:1987} and ALLFRAME \citep{Stetson:1994} suite of programs.

\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was used for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to the instrumental photometry to put our photometry on the PS1/DECam system. % ---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---
This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity. 
}

\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the g-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
We note that the smaller over-density located northeast of the \decam\ field, component b (see \figurename~\ref{fig:cmds}), was not followed up in this work.

% Notebook: Figure-DECam-CMD
\begin{figure}[t!]
\centering
\includegraphics[width=0.45\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus g color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

\begin{center}
\begin{deluxetable}{ccrrr}
\tablecaption{DECam Photometric Transformation\label{tbl:transphot}}
\tablecolumns{5}
\tablewidth{400pt}
\tablehead{
\colhead{Band} & \colhead{Color} & \colhead{Zero-point term} & \colhead{Color term}
}
\startdata
$u_{\rm DECam}$  &  \nodata & $27.178 \pm  0.016$ &     \nodata \\
$g_{\rm PS1}$  & $g_{\rm inst.}-i_{\rm inst.}$ & $24.9471 \pm  0.0068$  &     $-0.03494 \pm 0.0051$ \\
$i_{\rm PS1}$   &  $g_{\rm inst.}-i_{\rm inst.}$ & $24.7534 \pm 0.0011$ &     $-0.07379 \pm 0.0007$
\enddata
\end{deluxetable}
\end{center}

@@

While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
\changes{In addition, uncertainty in the \gaia\ passbands can cause significant differences in \gaia\ \bprp\ color for very blue sources \citep{MAW:2018}.}
To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
We note that this analysis and the subsequent discussion only considers subregion (a) of \clustername, which dominates the total mass and number of stars in the cluster.
\figurename~\ref{fig:decam-cmd} shows the \decam\ g- and i-band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
We use the g- and i-band photometry \changes{(and u-band, though only the brightest $\sim$15 cluster field members are robustly detected)} for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.
